---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

#Makes unique ids and combines
We added an extra column that just numbered all the way down for the amount of columns because we needed a unique attribute for when spreading
```{r}
making_uniqueID <- function(country){
  #Combines idnum and idnum_14 with "/" and then makes unique id
  country <- mutate(country,
                    idnum = ifelse(idnum_14 == '',
                                   idnum,
                                   paste(idnum,idnum_14,sep = "/")))
  
  mutate(country,
         unique_id = paste(
           paste(
             toupper(substr(pais, 1, 3)),
             substr(year, 3, 4), sep = ''),
           idnum, sep = "_"))
}

extra_id <- function(country) {
  i <- 1
  #Object column is the length of idnum column
  column <- length(country$idnum)
  #Repeats NA for length column
  number_for_dupID <- rep(NA, column)
  #Loop that adds row number
  while(i <= column){
    number_for_dupID[i] <- i
    i <- i + 1
  }
  number_for_dupID
}

full_id <- function(country){
  country <- making_uniqueID(country)
  extra_id <- extra_id(country)
  #Makes extra column, numbered by row
  country <- country %>%
    mutate(extra_id)
  country
}
  
countries <- list(argentina,belize, bolivia, brazil, canada, chile, colombia, costa, ecuador, elsalvador, guatemala, honduras, mexico, nicaragua, panama, peru, suriname, usa, uruguay, venezuela)
#Removed Guyan and Jamaica 6/27
  
#bolivia_test <- making_uniqueID(bolivia)
#bolivia_test %>% select(unique_id) %>% distinct  

argentina <- full_id(argentina)
belize <- full_id(belize)
bolivia <- full_id(bolivia)
brazil <- full_id(brazil)
canada <- full_id(canada)
chile <- full_id(chile)
colombia <- full_id(colombia)
costa <- full_id(costa)
ecuador <- full_id(ecuador)
elsalvador <- full_id(elsalvador)
guatemala <- full_id(guatemala)
#guyana <- full_id(guyana)
honduras <- full_id(honduras)
#jamaica <- full_id(jamaica)
mexico <- full_id(mexico)
nicaragua <- full_id(nicaragua)
panama <- full_id(panama)
paraguay <- full_id(paraguay)
peru <- full_id(peru)
suriname <- full_id(suriname)
usa <- full_id(usa)
uruguay <- full_id(uruguay)
venezuela <- full_id(venezuela)
```


Testing the ids with the data sets that we had problems with when spreading, this revealed that many had duplicate ids over the same year, so the data was not unique

Below, Bolivia's number of unique observations in the column unique_id is 18,003 when it should ideally have been 18,196 (total number of rows)
```{r}
bolivia_test <- making_uniqueID(bolivia)

bolivia_test %>%
  select(unique_id) %>%
  distinct()
```


Canada's ids are not unique, returns only 7,116 unique observations when it should be 7,151
```{r}
canada_test <- making_uniqueID(canada)

canada_test %>%
  select(unique_id) %>%
  distinct()
```


Not unique by two values
```{r}
colombia_test <- making_uniqueID(colombia)

colombia_test %>%
  select(unique_id) %>%
  distinct()
```


Not unique, 4,538 instead of 9,031
```{r}
costa_test <- making_uniqueID(costa)

costa_test %>%
  select(unique_id) %>%
  distinct()
```


Not unique by two values
```{r}
ecuador_test <- making_uniqueID(ecuador)

ecuador_test %>%
  select(unique_id) %>%
  distinct()
```


Not unique, 9,378 instead of 9,426
```{r}
elsalvador_test <- making_uniqueID(elsalvador)

elsalvador_test %>%
  select(unique_id) %>%
  distinct()
```


Not unique, 9,249 instead of 9,253
```{r}
guatemala_test <- making_uniqueID(guatemala)

guatemala_test %>%
  select(unique_id) %>%
  distinct()
```


Not unique by one observation
```{r}
honduras_test <- making_uniqueID(honduras)

honduras_test %>%
  select(unique_id) %>%
  distinct()
```


Not unique, 8,360 instead of 9,333
```{r}
mexico_test <- making_uniqueID(mexico)

mexico_test %>%
  select(unique_id) %>%
  distinct()
```

Not unique by one observation
```{r}
nicaragua_test <- making_uniqueID(nicaragua)

nicaragua_test %>%
  select(unique_id) %>%
  distinct()
```



UNIQUE - problem identified, because of the two columns vb11_10 and vb11_12
```{r}
usa_test <- making_uniqueID(usa)

usa_test %>%
  select(unique_id) %>%
  distinct()
```

I did notice though that the first three letters for unique_id for USA isa EST for some reason?? Will look into later



