---
title: "Assert tests"
output: html_notebook
---

```{r}
library(tidyverse)
library(assertr)
```

#Test for uniqueness of idnum

```{r}
guatemala %>% assert(is_uniq, idnum)
```

idnum is not unique, not necessarily people but number of the questionnaire

#Correct   
```{r}
estrato <- c("Metropolitana", "Suroriente", "Nororiente", "Noroccidente", "Suroccidente", "Sur")

guatemala %>% assert(in_set(estrato), estratopri)

venezuela %>% assert(in_set(estrato), estratopri)

```

estratopri was as expected, each country has a different unique set of variables

```{r}
gender <- c("Hombre", "Mujer")

gender_eng <- c("Male", "Female")

guatemala %>% assert(in_set(gender), q1)

guyana %>% assert(in_set(gender_eng), q1)
```

gender was what was expected, there are only two options, and none of them are left blank

```{r}
#venezuela %>% verify((q1))

#class(guatemala$q1)

#guat2 <- guatemala %>% group_by(year) %>% mutate(mean_age = mean(q2))

class(brazil_new$q1)

#str(brazil_new)
str(brazil)

```


Everything after idnum_14 is a factor, so no math can be done on any values like age, and can't check if all the columns are characters or numeric values - we have already noticed that there are some numeric values in columns like estratopri for venezuela where it should be a character

```{r}
q <- c("Not asked in this country or year")
guyana %>% filter(year == 2006) %>% assert(in_set(q), estratosec)

qs <- c("No se le preguntó en este país o año")
venezuela %>% filter(year == 2008) %>% assert(in_set(qs), estratosec)
```


should we change the columns that have "Not asked in this country or year" to NA values?




