---
title: "finding columns to unfactor"
output: html_notebook
---
FIRST
THIS all has to happen first, and then 2 etc....

the beginnings of trying to figure out how to identify columns that have specific values
```{r}
library(glue)
unfactor <- rep(NA, 152)
i <- 1
find_col_to_unfactor <- function(country){
  for(x in length(all_common_col)){
    if(1 %in% (country %>% select(!!! syms(all_common_col[x]))) ){
    unfactor[i] <- all_common_col[x]
    i <-  i + 1
    }
  }
  return(unfactor)
}

```


Jackpot - was able to make a list of all the columns that have 6 in them, by using [[]] to get right to the column, could probably simplify that first line after the while loop, but it works for now - and now need to think about maybe how to search for multiple things at one, like 6,7,8 all at once. then need to seperate so things can be factored and then combine back together
```{r}
unfactor <- rep(NA, 152)
df <- data_frame()
i <- 1
x <- 1
find_col_to_unfactor2 <- function(country){
  while(x <= length(all_common_col)){
    d <- (country %>% select(!!! syms(all_common_col[x])))
    if(6 %in% d[[unlist(all_common_col[x])]]){
      unfactor[i] <- all_common_col[x]
      i <-  i + 1
    }
    x <-  x + 1
  }
  return(unfactor)
}
```


trying to figure out how to seperate columns that don't need to be factored into one dataframe, and removing from other. Currently it is returning a dataframe with the remaining columns that have been left after the ones not needing to be factored are removed, the unfactored types are in data frame named df
```{r}
factor <- rep(NA, 152)
i <- 1
x <- 1
find_col_to_unfactor3 <- function(country){
  unfactor <- data_frame(country$pais)
  while(x <= length(all_common_col)){
    d <- (country %>% select(!!! syms(all_common_col[x])))
    if(6 %in% d[[unlist(all_common_col[x])]] || 7 %in% d[[unlist(all_common_col[x])]] || 8 %in% d[[unlist(all_common_col[x])]] || 9 %in% d[[unlist(all_common_col[x])]] || 10 %in% d[[unlist(all_common_col[x])]]){
      unfactor <- cbind(unfactor, d)
    }
    else{
      factor[i] <- unlist(all_common_col[x])
      i <- i + 1
    }
    x <-  x + 1
  }
  factor <- factor[!is.na(factor)]
  country[factor]
  return(country)
}
```

combines together succesfully!! This also takes care of shrink, so that it no longer needs to be its own seperate function, but have to have all_common_col initialized so that it can be done
```{r}
factor_country <- function(country) {
  country_factor <- as_factor(country)
  return(country_factor)
}

factor <- rep(NA, 152)
i <- 1
x <- 1
factor_unfactor_combine <- function(filename){
  country <- read_dta(filename)
  unfactor <- data_frame('extra' = country$pais)
  while(x <= length(all_common_col)){
    d <- (country %>% select(!!! syms(all_common_col[x])))
    if(6 %in% d[[unlist(all_common_col[x])]] || 7 %in% d[[unlist(all_common_col[x])]] || 8 %in% d[[unlist(all_common_col[x])]] || 9 %in% d[[unlist(all_common_col[x])]] || 10 %in% d[[unlist(all_common_col[x])]]){
      unfactor <- cbind(unfactor, d)
    }
    else{
      factor[i] <- unlist(all_common_col[x])
      i <- i + 1
    }
    x <-  x + 1
  }
  unfactor <- unfactor %>% select(-extra)
  factor <- factor[!is.na(factor)]
  country <- country[factor]
  factored_country <- factor_country(country)
  full_country <- cbind(factored_country, unfactor)
  return(full_country)
}
```

```{r}
argentina <- factor_unfactor_combine("1326054827Argentina LAPOP merge 2008-2014 v3.0_W_dta.zip")
bolivia <- factor_unfactor_combine("1500779614Bolivia LAPOP merge 2004-2014 v3.0_W_dta.zip")
brazil <- factor_unfactor_combine("1058457654Brazil LAPOP merge 2007-2014 v3.0_W_dta.zip")
belize <- factor_unfactor_combine("1866361808Belize LAPOP merge 2008-2014 v3.0_W_dta.zip")
canada <- factor_unfactor_combine("257165704Canada LAPOP merge 2006-2014 v3.0_W_dta.zip")
chile <- factor_unfactor_combine("1651690880Chile LAPOP merge 2006-2014 v3.0_W_dta.zip")
colombia <- factor_unfactor_combine("26761406Colombia LAPOP merge 2004-2014 v3.0_W_dta.zip")
costa <- factor_unfactor_combine("312640706CostaRica LAPOP merge 2004-2014 v3.0_W_dta.zip")
ecuador <- factor_unfactor_combine("1562314955Ecuador LAPOP merge 2004-2014 v3.0_W_dta.zip")
elsalvador <- factor_unfactor_combine("71618678ElSalvador LAPOP merge 2004-2014 v3.0_W_dta.zip")
guatemala <- factor_unfactor_combine("833541857Guatemala LAPOP merge 2004-2014 v3.0_W_dta.zip")
guyana <- factor_unfactor_combine("1293237393Guyana LAPOP merge 2006-2014 v3.0_W_dta.zip")
paraguay <- factor_unfactor_combine("450650714Paraguay LAPOP merge 2006-2014 v3.0_W_dta.zip")
honduras <- factor_unfactor_combine("125162980Honduras LAPOP merge 2004-2014 v3.0_W_dta.zip")
jamaica <- factor_unfactor_combine("1518553693Jamaica LAPOP merge 2006-2014 v3.0_W_dta.zip")
mexico <- factor_unfactor_combine("1467358429Mexico LAPOP merge 2004-2014 v3.0_W_dta.zip")
nicaragua <- factor_unfactor_combine("420919900Nicaragua LAPOP merge 2004-2014 v3.0_W_dta.zip")
panama <- factor_unfactor_combine("1909860951Panama LAPOP merge 2004-2014 v3.0_W_dta.zip")
peru <- factor_unfactor_combine("897206140Peru LAPOP merge 2006-2014 v3.0_W_dta.zip")
suriname <- factor_unfactor_combine("2028239474Suriname LAPOP merge 2010-2014 v3.0_W_dta.zip")
usa <- factor_unfactor_combine("1355754260UnitedStates LAPOP merge 2006-2014 v3.0_W_dta.zip")
uruguay <- factor_unfactor_combine("1222977998Uruguay LAPOP merge 2007-2014 v3.0_W_dta.zip")
venezuela <- factor_unfactor_combine("1165310382Venezuela LAPOP merge 2007-2014 v3.0_W_dta.zip")
```

!!!USE THIS ONE!!!
I tested out the above and something went wrong in step 6 so I'm testing other ways to go about it
```{r}
factor_country <- function(country) {
  country_factor <- as_factor(country)
  return(country_factor)
}

factor <- rep(NA, 152)
i <- 1
x <- 1
factor_unfactor_combine2 <- function(filename){
  country <- read_dta(filename)
  columns <- attributes(country)$names
  unfactor <- data_frame('extra' = country$pais)
  while(x <= length(columns)){
    d <- (country %>% select(!!! syms(columns[x])))
    if(6 %in% d[[unlist(columns[x])]] || 7 %in% d[[unlist(columns[x])]] || 8 %in% d[[unlist(columns[x])]] || 9 %in% d[[unlist(columns[x])]] || 10 %in% d[[unlist(columns[x])]]){
      unfactor <- cbind(unfactor, d)
    }
    else{
      factor[i] <- unlist(columns[x])
      i <- i + 1
    }
    x <-  x + 1
  }
  unfactor <- unfactor %>% select(-extra)
  factor <- factor[!is.na(factor)]
  country <- country[factor]
  factored_country <- factor_country(country)
  full_country <- cbind(factored_country, unfactor)
  return(full_country)
}
```

```{r}
argentina <- factor_unfactor_combine2("1326054827Argentina LAPOP merge 2008-2014 v3.0_W_dta.zip")
bolivia <- factor_unfactor_combine2("1500779614Bolivia LAPOP merge 2004-2014 v3.0_W_dta.zip")
brazil <- factor_unfactor_combine2("1058457654Brazil LAPOP merge 2007-2014 v3.0_W_dta.zip")
belize <- factor_unfactor_combine2("1866361808Belize LAPOP merge 2008-2014 v3.0_W_dta.zip")
canada <- factor_unfactor_combine2("257165704Canada LAPOP merge 2006-2014 v3.0_W_dta.zip")
chile <- factor_unfactor_combine2("1651690880Chile LAPOP merge 2006-2014 v3.0_W_dta.zip")
colombia <- factor_unfactor_combine2("26761406Colombia LAPOP merge 2004-2014 v3.0_W_dta.zip")
costa <- factor_unfactor_combine2("312640706CostaRica LAPOP merge 2004-2014 v3.0_W_dta.zip")
ecuador <- factor_unfactor_combine2("1562314955Ecuador LAPOP merge 2004-2014 v3.0_W_dta.zip")
elsalvador <- factor_unfactor_combine2("71618678ElSalvador LAPOP merge 2004-2014 v3.0_W_dta.zip")
guatemala <- factor_unfactor_combine2("833541857Guatemala LAPOP merge 2004-2014 v3.0_W_dta.zip")
guyana <- factor_unfactor_combine2("1293237393Guyana LAPOP merge 2006-2014 v3.0_W_dta.zip")
paraguay <- factor_unfactor_combine2("450650714Paraguay LAPOP merge 2006-2014 v3.0_W_dta.zip")
honduras <- factor_unfactor_combine2("125162980Honduras LAPOP merge 2004-2014 v3.0_W_dta.zip")
jamaica <- factor_unfactor_combine2("1518553693Jamaica LAPOP merge 2006-2014 v3.0_W_dta.zip")
mexico <- factor_unfactor_combine2("1467358429Mexico LAPOP merge 2004-2014 v3.0_W_dta.zip")
nicaragua <- factor_unfactor_combine2("420919900Nicaragua LAPOP merge 2004-2014 v3.0_W_dta.zip")
panama <- factor_unfactor_combine2("1909860951Panama LAPOP merge 2004-2014 v3.0_W_dta.zip")
peru <- factor_unfactor_combine2("897206140Peru LAPOP merge 2006-2014 v3.0_W_dta.zip")
suriname <- factor_unfactor_combine2("2028239474Suriname LAPOP merge 2010-2014 v3.0_W_dta.zip")
usa <- factor_unfactor_combine2("1355754260UnitedStates LAPOP merge 2006-2014 v3.0_W_dta.zip")
uruguay <- factor_unfactor_combine2("1222977998Uruguay LAPOP merge 2007-2014 v3.0_W_dta.zip")
venezuela <- factor_unfactor_combine2("1165310382Venezuela LAPOP merge 2007-2014 v3.0_W_dta.zip")
```


```{r}
argentina_test <- factor_unfactor_combine2(argentina)
bolivia_test <- factor_unfactor_combine2(bolivia)
brazil_test <- factor_unfactor_combine2(brazil)
belize_test <- factor_unfactor_combine2(belize)
canada_test <- factor_unfactor_combine2(canada)
chile_test <- factor_unfactor_combine2(chile)
colombia_test <- factor_unfactor_combine2(colombia)
costa_test <- factor_unfactor_combine2(costa)
ecuador_test <- factor_unfactor_combine2(ecuador)
elsalvador_test <- factor_unfactor_combine2(elsalvador)
guatemala_test <- factor_unfactor_combine2(guatemala)
guyana_test <- factor_unfactor_combine2(guyana)
paraguay_test <- factor_unfactor_combine2(paraguay)
honduras_test <- factor_unfactor_combine2(honduras)
jamaica_test <- factor_unfactor_combine2(jamaica)
mexico_test <- factor_unfactor_combine2(mexico)
nicaragua_test <- factor_unfactor_combine2(nicaragua)
panama_test <- factor_unfactor_combine2(panama)
peru_test <- factor_unfactor_combine2(peru)
suriname_test <- factor_unfactor_combine2(suriname)
usa_test <- factor_unfactor_combine2(usa)
uruguay_test <- factor_unfactor_combine2(uruguay)
venezuela_test <- factor_unfactor_combine2(venezuela)
```

```{r}
attributes(argentina)$names
```


Random tests
```{r}
d <- argentina_before %>% select(!!! syms(all_common_col[1]))
as.name(unlist(all_common_col[1]))
x <- as.name(unlist(all_common_col[1]))
d$as.name(unlist(all_common_col[1]))
17 %in% argentina_before$pais
```

```{r}

argentina_before$x
```


```{r}
unlist(all_common_col[1])
og <- as.name(unlist(all_common_col[1]))
argentina %>% select(og)
```



```{r}
df %>% mutate(country %>% select({{all_common_col[x]}})) 
country %>% remove(country %>% select({{all_common_col[x]}}))
```

