---
title: "Finding Similar Column Names"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

##Bolivia
```{r, message=FALSE}
library(dplyr)
library(haven)

bolivia_merged <- read_dta("1500779614Bolivia LAPOP merge 2004-2014 v3.0_W_dta.zip")

#Factors Bolivia merged data set
bolivia_factor <- as_factor(bolivia_merged)
```

##Duplicated ID

We thought ID was duplicated between id and id_14. Is this true for all countries? What creates a unique identifier we can join prior to 2014. duplicated estropri and prov

```{r, message=FALSE}
library(dplyr)

#Shows first 6 idnum observations
bolivia_factor %>%
  select(idnum) %>%
  head()

#Shows blank observations before year 2014
bolivia_factor %>%
  select(idnum_14) %>%
  head()

#Shows last 6 
bolivia_factor %>%
  select(idnum) %>%
  tail()

#idnum_14 begins to have observations
bolivia_factor %>%
  select(idnum_14) %>%
  tail()
```


##Unique
Investigating unique keys for combining data files
```{r}
bolivia_factor %>%
  select(idnum, upm) %>%
  distinct()
```

##Brazil

```{r, message=FALSE}
library(dplyr)
library(haven)

#Loads in Brazil merged file
brazil_merged <- read_dta("1058457654Brazil LAPOP merge 2007-2014 v3.0_W_dta.zip")

brazil_factor <- as_factor(brazil_merged)
```

##Observations
Some observations are in Spanish, some in Portuguese. Might be because it was only asked in that country.

```{r}
brazil_factor %>%
  select(aut1) %>%
  head()

bolivia_factor %>%
  select(aut1) %>%
  head()
```

There are 753 columns for Bolivia, but 808 in Brazil.

Noticed in columns beginning with b1, observations are a mix of strings (No Aplica, Nada, Mucho) and integers (2-6). Seems to be measuring a scale

```{r}
brazil_factor %>%
  select(b2) %>%
  head()
```

Should change "No Aplica" to "NA".


##Canada

```{r, message=FALSE}
library(dplyr)
library(haven)

#Loads in Canada merged file
canada_merged <- read_dta("257165704Canada LAPOP merge 2006-2014 v3.0_W_dta.zip")

canada_factor <- as_factor(canada_merged)
```

Only 262 columns, answers and most labels are in Spanish. Some of both are in English later on. Some numbers are written out some and some use digits.



```{r}
library(dplyr)
canada_factor %>%
  filter(year == 2008) %>%
  select(cancsize) %>%
  head()
#starts in the year 2008
```


##Finding Column Similarities
Currently beginning to compare common questions that were asked across different countries.
```{r}
factor_country <- function(filename) {
  library(haven)
  library(dplyr)
  country_merged <- read_dta(filename)
  country_factor <- as_factor(country_merged)
  return(country_factor)
}
#Choosing column names by country
colnames_bol <- attributes(bolivia_factor)$names
colnames_bra <- attributes(brazil_factor)$names

#Function for comparing column names
same_column_names <- function(country1, country2) {
  #Collects names of each column from their respective data set
  list1 <- attributes(country1)$names 
  list2 <- attributes(country2)$names
  #Initializing list
  firstlist <- vector("list", 800)

  i <- 1
  n <- 0
  k <- 1

  #Looping through both column names to find similarities
  for (name1 in list1) {
    for (name2 in list2) {
      if (name1 == name2) {
        firstlist[[i]] <- name1
        i <- i + 1
      }
    }
  }


  #Getting rid of NULL values
  for(x in firstlist){
    if(is.null(x) == FALSE) {
     n <- n + 1
    }
  }
 
  final <- vector("list", n)

  for(x in firstlist) {
    final[[k]] <- x
    k <- k + 1
  }

  #Print result
  return(final)
}

same_column_names(factor_country("1326054827Argentina LAPOP merge 2008-2014 v3.0_W_dta.zip"), factor_country("71618678ElSalvador LAPOP merge 2004-2014 v3.0_W_dta.zip"))

```

Looking for the smallest column number and the largest. 

##Function for as_factor()
```{r}
factor_country <- function(filename) {
  country_merged <- read_dta(filename)
  country_factor <- as_factor(country_merged)
  return(country_factor)
}
```

##Loading in Countries
```{r}
library(haven)
argentina <- factor_country("1326054827Argentina LAPOP merge 2008-2014 v3.0_W_dta.zip")
bolivia <- factor_country("1500779614Bolivia LAPOP merge 2004-2014 v3.0_W_dta.zip")
brazil <- factor_country("1058457654Brazil LAPOP merge 2007-2014 v3.0_W_dta.zip")
belize <- factor_country("1866361808Belize LAPOP merge 2008-2014 v3.0_W_dta.zip")
canada <- factor_country("257165704Canada LAPOP merge 2006-2014 v3.0_W_dta.zip")
chile <- factor_country("1651690880Chile LAPOP merge 2006-2014 v3.0_W_dta.zip")
colombia <- factor_country("26761406Colombia LAPOP merge 2004-2014 v3.0_W_dta.zip")
costa <- factor_country("312640706CostaRica LAPOP merge 2004-2014 v3.0_W_dta.zip")
ecuador <- factor_country("1562314955Ecuador LAPOP merge 2004-2014 v3.0_W_dta.zip")
elsalvador <- factor_country("71618678ElSalvador LAPOP merge 2004-2014 v3.0_W_dta.zip")
guatemala <- factor_country("833541857Guatemala LAPOP merge 2004-2014 v3.0_W_dta.zip")
guyana <- factor_country("1293237393Guyana LAPOP merge 2006-2014 v3.0_W_dta.zip")
```

##Number of Columns
Argentina: 513 *
Belize: 482 *
Bolivia: 753 *
Brazil: 808 *
Canada: 262 *
Chile: 740 *
Colombia: 810 *
Costa Rica: 729
Ecuador: 695 *
El Salvador: 685 *
Guatemala: 699 *
Guyana: 551 *

```{r}
canada_brazil <- same_column_names(canada_factor, brazil_factor)

list_and_factor <- function(list1, country2) {
  #Collects names of each column from their respective data set
  list2 <- attributes(country2)$names
  #Initializing list
  firstlist <- vector("list", 800)

  i <- 1
  n <- 0
  k <- 1

  #Looping through both column names to find similarities
  for (name1 in list1) {
    for (name2 in list2) {
      if (name1 == name2) {
        firstlist[[i]] <- name1
        i <- i + 1
      }
    }
  }


  #Getting rid of NULL values
  for(x in firstlist){
    if(is.null(x) == FALSE) {
     n <- n + 1
    }
  }
 
  final <- vector("list", n)

  for(x in firstlist) {
    final[[k]] <- x
    k <- k + 1
  }

  #Print result
  return(final)
}

can_bra_bol <- list_and_factor(canada_brazil, bolivia) #199
can_bra_bol_chi <- list_and_factor(can_bra_bol, chile) #199
can_bra_bol_chi_col <- list_and_factor(can_bra_bol_chi, colombia) #199
after_colombia <- list_and_factor(can_bra_bol_chi_col, belize) #197
after_belize <- list_and_factor(after_colombia, guyana) #196
after_guyana <- list_and_factor(after_belize, argentina) #194
after_argentina <- list_and_factor(after_guyana, elsalvador) #194
after_elsalvador <- list_and_factor(after_argentina, ecuador) #194
after_ecuador <- list_and_factor(after_elsalvador, guatemala) #194
final_comparison <- list_and_factor(after_ecuador, costa) #193

#Loading in Remaining countries

honduras <- factor_country("125162980Honduras LAPOP merge 2004-2014 v3.0_W_dta.zip")
jamaica <- factor_country("1518553693Jamaica LAPOP merge 2006-2014 v3.0_W_dta.zip")
mexico <- factor_country("1467358429Mexico LAPOP merge 2004-2014 v3.0_W_dta.zip")
nicaragua <- factor_country("420919900Nicaragua LAPOP merge 2004-2014 v3.0_W_dta.zip")
panama <- factor_country("1909860951Panama LAPOP merge 2004-2014 v3.0_W_dta.zip")
peru <- factor_country("897206140Peru LAPOP merge 2006-2014 v3.0_W_dta.zip")
suriname <- factor_country("2028239474Suriname LAPOP merge 2010-2014 v3.0_W_dta.zip")
usa <- factor_country("1355754260UnitedStates LAPOP merge 2006-2014 v3.0_W_dta.zip")
uruguay <- factor_country("1222977998Uruguay LAPOP merge 2007-2014 v3.0_W_dta.zip")
venezuela <- factor_country("1165310382Venezuela LAPOP merge 2007-2014 v3.0_W_dta.zip")
```

```{r}
#Now we will compare my final object with Lindsay's

#Importing Lindsay's list
library(readr)
lindsay_final <- read_csv("last.csv")

#Function to compare lists
list_and_list <- function(list1, list2) {
  #Initializing list
  firstlist <- vector("list", 800)

  i <- 1
  n <- 0
  k <- 1

  #Looping through both column names to find similarities
  for (name1 in list1) {
    for (name2 in list2) {
      if (name1 == name2) {
        firstlist[[i]] <- name1
        i <- i + 1
      }
    }
  }


  #Getting rid of NULL values
  for(x in firstlist){
    if(is.null(x) == FALSE) {
     n <- n + 1
    }
  }
 
  final <- vector("list", n)

  for(x in firstlist) {
    final[[k]] <- x
    k <- k + 1
  }

  #Print result
  return(final)
}

all_common_col <- list_and_list(final_comparison, lindsay_final) #152

all_common_col
```