---
title: "Fixing Ordinal Values"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

##Exploring structure of columns with ordinal values
Looking to see what the structure of the factored version of Argentina shows for likert scale.

```{r}
attributes(argentina$d1)
```
This column uses 10-point scalewith additional opt-out answers "No Sabe" and "No Responde". 2-9 are numeric, but 1 and 10 have anchors that are text. This is what hinders graphing in Tableau.

Will look for columns that use different number scales before attempting to edit the anchors.

```{r}
attributes(argentina$b1)
```

This column has 7-point scale, from "Nada" (1) to "Mucho" (7). Again, 2-6 numeric, but text anchors. Also includes "No Sabe" and "No repsonde". Should these later be turned into NA, or should it remain separate?

```{r}
attributes(argentina$b31)
```

7-point scale.

I was concerned that there could be a wide variety of anchors, but I remembered that the questionnaires used provide cards for all likert scale questions. There are avaiable on the (LAPOP Website)[https://www.vanderbilt.edu/lapop/core-surveys.php]

I will be using the Core Questionnaires to get the possible answers.

##Possible Scale Outcomes
Not sure about capitalizations of the words.

#2004
Card A:
1 = "Not at all", 7 = "A lot"
1 = "Nada", 7 = "Mucho"

Card B:
1 = "Strongly Disagree", 7 = "Strongly Agree"
1 = "Muy de Desacuerdo", 7 = "Muy de Acuerdo"

Card C:
1 = "Firmly Disapprove", 10 = "Firmly Approves"
1 = "Desaprueba Firmemente", 10 = "Aprueba Firmememnte"

Card D:
1 = "Very Corrupt", 10 = "Very Honest"
1 = "Muy Corruptos", 10 = "Muy Honrados"

Card E:
1 = "Left", 10 = "Right"
1 = "Izquierda", 10 = "Derecha"

#2006
Cards A and B the same
Card 1 = Card E
No D
Card C (English only):
1 = "Strongly Disapprove", 10 = "Strongly Approve"

#2008
Card 1 = Card E
A - C same
Card D:
1 = "Worst Life Possible", 10 = "Best Life Possible"
0 = "Peor Vida Posible", 10 = "Mejor Vida Posible"

This is weird that they did different scales for different languages?? Not sure why this would be necessary, and also they changed it in the following year?

#2010
Card A:
0 = "Worst Life Possible", 10 = "Best Life Possible"
0 = "La Peor Vida Posible", 10 = "La Mejor Vida Posible"

Card B:
Added in addition to previous Left-Right scales
1 = "Liberal", 10 = "Conservative"
1 = "Liberal", 10 = "Conservador"

#2012
Card E:
1 = "Defends the Rich", 10 = "Defends the poor"
1 = "Defiende a los ricos", 10 = "Defiende a los pobres"

#2014
No differences from above.

#2016/17
Card N:
1 = "Environment is priority", 10 = "Economic growth is priority"
1 = "Medio ambiente es prioridad", 10 = "Crecimiento económico es prioridad"

