---
title: "Fixing Ordinal Values"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

##Exploring structure of columns with ordinal values
Looking to see what the structure of the factored version of Argentina shows for likert scale.

```{r}
attributes(argentina$d1)
```
This column uses 10-point scalewith additional opt-out answers "No Sabe" and "No Responde". 2-9 are numeric, but 1 and 10 have anchors that are text. This is what hinders graphing in Tableau.

Will look for columns that use different number scales before attempting to edit the anchors.

```{r}
attributes(argentina$b1)
```

This column has 7-point scale, from "Nada" (1) to "Mucho" (7). Again, 2-6 numeric, but text anchors. Also includes "No Sabe" and "No repsonde". Should these later be turned into NA, or should it remain separate?

```{r}
attributes(argentina$b31)
```

7-point scale.

I was concerned that there could be a wide variety of anchors, but I remembered that the questionnaires used provide cards for all likert scale questions. There are avaiable on the (LAPOP Website)[https://www.vanderbilt.edu/lapop/core-surveys.php]

I will be using the Core Questionnaires to get the possible answers.

##Possible Scale Outcomes
Not sure about capitalizations of the words.

#2004
Card A:
1 = "Not at all", 7 = "A lot"
1 = "Nada", 7 = "Mucho"

Card B:
1 = "Strongly Disagree", 7 = "Strongly Agree"
1 = "Muy de Desacuerdo", 7 = "Muy de Acuerdo"

Card C:
1 = "Firmly Disapprove", 10 = "Firmly Approves"
1 = "Desaprueba Firmemente", 10 = "Aprueba Firmememnte"

Card D:
1 = "Very Corrupt", 10 = "Very Honest"
1 = "Muy Corruptos", 10 = "Muy Honrados"

Card E:
1 = "Left", 10 = "Right"
1 = "Izquierda", 10 = "Derecha"

#2006
Cards A and B the same
Card 1 = Card E
No D
Card C (English only):
1 = "Strongly Disapprove", 10 = "Strongly Approve"

#2008
Card 1 = Card E
A - C same
Card D:
1 = "Worst Life Possible", 10 = "Best Life Possible"
0 = "Peor Vida Posible", 10 = "Mejor Vida Posible"

This is weird that they did different scales for different languages?? Not sure why this would be necessary, and also they changed it in the following year?

#2010
Card A:
0 = "Worst Life Possible", 10 = "Best Life Possible"
0 = "La Peor Vida Posible", 10 = "La Mejor Vida Posible"

Card B:
Added in addition to previous Left-Right scales
1 = "Liberal", 10 = "Conservative"
1 = "Liberal", 10 = "Conservador"

#2012
Card E:
1 = "Defends the Rich", 10 = "Defends the poor"
1 = "Defiende a los ricos", 10 = "Defiende a los pobres"

#2014
No differences from above.

#2016/17
Card N:
1 = "Environment is priority", 10 = "Economic growth is priority"
1 = "Medio ambiente es prioridad", 10 = "Crecimiento económico es prioridad"

After pulling factored and unfactored data into Tableau, we noticed that there is an issue with different languages. I am going to pull out the data sets that are written in English only to prevent conflicts when graphing. Will check in with LAPOP folks about getting data that is in one language only.

I will be removing Guyana and Jamaica from the common columns.


##Finding Column Similarities
Currently beginning to compare common questions that were asked across different countries.
```{r}
factor_country <- function(filename) {
  library(haven)
  library(dplyr)
  country_merged <- read_dta(filename)
  nums <- country_merged %>%
    select(year, q2)
  other <- country_merged %>%
    select(-year,-q2)
  other <- as_factor(other)
  other <- cbind(nums, other)
  other
}
#Choosing column names by country
colnames_bol <- attributes(bolivia_factor)$names
colnames_bra <- attributes(brazil_factor)$names

#Function for comparing column names
same_column_names <- function(country1, country2) {
  #Collects names of each column from their respective data set
  list1 <- attributes(country1)$names 
  list2 <- attributes(country2)$names
  #Initializing list
  firstlist <- vector("list", 800)

  i <- 1
  n <- 0
  k <- 1

  #Looping through both column names to find similarities
  for (name1 in list1) {
    for (name2 in list2) {
      if (name1 == name2) {
        firstlist[[i]] <- name1
        i <- i + 1
      }
    }
  }


  #Getting rid of NULL values
  for(x in firstlist){
    if(is.null(x) == FALSE) {
     n <- n + 1
    }
  }
 
  final <- vector("list", n)

  for(x in firstlist) {
    final[[k]] <- x
    k <- k + 1
  }

  #Print result
  return(final)
}

same_column_names(factor_country("1326054827Argentina LAPOP merge 2008-2014 v3.0_W_dta.zip"), factor_country("71618678ElSalvador LAPOP merge 2004-2014 v3.0_W_dta.zip"))
```

Looking for the smallest column number and the largest. 

##Function for as_factor()
```{r}
factor_country <- function(filename) {
  country_merged <- read_dta(filename)
  country_factor <- as_factor(country_merged)
  return(country_factor)
}
```

##Loading in Countries
```{r}
library(haven)
argentina <- factor_country("1326054827Argentina LAPOP merge 2008-2014 v3.0_W_dta.zip")
bolivia <- factor_country("1500779614Bolivia LAPOP merge 2004-2014 v3.0_W_dta.zip")
brazil <- factor_country("1058457654Brazil LAPOP merge 2007-2014 v3.0_W_dta.zip")
belize <- factor_country("1866361808Belize LAPOP merge 2008-2014 v3.0_W_dta.zip")
canada <- factor_country("257165704Canada LAPOP merge 2006-2014 v3.0_W_dta.zip")
chile <- factor_country("1651690880Chile LAPOP merge 2006-2014 v3.0_W_dta.zip")
colombia <- factor_country("26761406Colombia LAPOP merge 2004-2014 v3.0_W_dta.zip")
costa <- factor_country("312640706CostaRica LAPOP merge 2004-2014 v3.0_W_dta.zip")
ecuador <- factor_country("1562314955Ecuador LAPOP merge 2004-2014 v3.0_W_dta.zip")
elsalvador <- factor_country("71618678ElSalvador LAPOP merge 2004-2014 v3.0_W_dta.zip")
guatemala <- factor_country("833541857Guatemala LAPOP merge 2004-2014 v3.0_W_dta.zip")
guyana <- factor_country("1293237393Guyana LAPOP merge 2006-2014 v3.0_W_dta.zip")
paraguay <- factor_country("450650714Paraguay LAPOP merge 2006-2014 v3.0_W_dta.zip") #added 6/24
```

##Number of Columns
Argentina: 513 *
Belize: 482 *
Bolivia: 753 *
Brazil: 808 *
Canada: 262 *
Chile: 740 *
Colombia: 810 *
Costa Rica: 729
Ecuador: 695 *
El Salvador: 685 *
Guatemala: 699 *
Guyana: 551 *
Paraguay: 553

```{r}
canada_brazil <- same_column_names(canada_factor, brazil_factor)

list_and_factor <- function(list1, country2) {
  #Collects names of each column from their respective data set
  list2 <- attributes(country2)$names
  #Initializing list
  firstlist <- vector("list", 800)

  i <- 1
  n <- 0
  k <- 1

  #Looping through both column names to find similarities
  for (name1 in list1) {
    for (name2 in list2) {
      if (name1 == name2) {
        firstlist[[i]] <- name1
        i <- i + 1
      }
    }
  }


  #Getting rid of NULL values
  for(x in firstlist){
    if(is.null(x) == FALSE) {
     n <- n + 1
    }
  }
 
  final <- vector("list", n)

  for(x in firstlist) {
    final[[k]] <- x
    k <- k + 1
  }

  #Print result
  return(final)
}

can_bra_bol <- list_and_factor(canada_brazil, bolivia) #199
can_bra_bol_chi <- list_and_factor(can_bra_bol, chile) #199
can_bra_bol_chi_col <- list_and_factor(can_bra_bol_chi, colombia) #199
after_colombia <- list_and_factor(can_bra_bol_chi_col, belize) #197
after_belize <- list_and_factor(after_colombia, argentina) #196 
after_argentina <- list_and_factor(after_guyana, elsalvador) #194
after_elsalvador <- list_and_factor(after_argentina, ecuador) #194
after_ecuador <- list_and_factor(after_elsalvador, guatemala) #194
after_guatemala <- list_and_factor(after_ecuador, costa) #193
final_comparison <- list_and_factor(after_guatemala, paraguay) #193

#Loading in Remaining countries

honduras <- factor_country("125162980Honduras LAPOP merge 2004-2014 v3.0_W_dta.zip") #Didn't load in Jamaica
mexico <- factor_country("1467358429Mexico LAPOP merge 2004-2014 v3.0_W_dta.zip")
nicaragua <- factor_country("420919900Nicaragua LAPOP merge 2004-2014 v3.0_W_dta.zip")
panama <- factor_country("1909860951Panama LAPOP merge 2004-2014 v3.0_W_dta.zip")
peru <- factor_country("897206140Peru LAPOP merge 2006-2014 v3.0_W_dta.zip")
suriname <- factor_country("2028239474Suriname LAPOP merge 2010-2014 v3.0_W_dta.zip")
usa <- factor_country("1355754260UnitedStates LAPOP merge 2006-2014 v3.0_W_dta.zip")
uruguay <- factor_country("1222977998Uruguay LAPOP merge 2007-2014 v3.0_W_dta.zip")
venezuela <- factor_country("1165310382Venezuela LAPOP merge 2007-2014 v3.0_W_dta.zip")
```

```{r}
#Now we will compare my final object with Lindsay's

#Importing Lindsay's list
library(readr)
lindsay_final <- read_csv("last.csv")

#Function to compare lists
list_and_list <- function(list1, list2) {
  #Initializing list
  firstlist <- vector("list", 800)

  i <- 1
  n <- 0
  k <- 1

  #Looping through both column names to find similarities
  for (name1 in list1) {
    for (name2 in list2) {
      if (name1 == name2) {
        firstlist[[i]] <- name1
        i <- i + 1
      }
    }
  }


  #Getting rid of NULL values
  for(x in firstlist){
    if(is.null(x) == FALSE) {
     n <- n + 1
    }
  }
 
  final <- vector("list", n)

  for(x in firstlist) {
    final[[k]] <- x
    k <- k + 1
  }

  #Print result
  return(final)
}

lindsay_final <- read_csv("last.csv")

all_common_col <- list_and_list(final_comparison, lindsay_final) #152


#common_2016_2017_and_before <- list_and_list(all_common_col, final_sixteen)
#common_2016_2017_and_before
```




