---
title: "Reformatting Try Function"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---
#Lengthen Function
```{r, message = FALSE}
library(tidyverse)
library(devtools)
library(fs)

#Function for reducing columns
lengthen <- function(country) {
  country <- country %>%
  select(-strata) %>%
  gather(column_name, answer, estratopri:gi7r) %>%
  select(pais, year, unique_id, column_name, answer)
  return(country)
}
```

##Applying above function to every country
Adds all the countries, in correct tidy format into a large data set
```{r}
library(purrr)
argentina_and_belize <- list(argentina, belize)
argentina_and_belize <- map_df(argentina_and_belize, lengthen)

bolivia_and_brazil <- list(bolivia, brazil)
bolivia_and_brazil <- map_df(bolivia_and_brazil, lengthen)

canada_and_chile <- list(canada, chile)
canada_and_chile <- map_df(canada_and_chile, lengthen)

colombia_and_costa <- list(colombia, costa)
colombia_and_costa <- map_df(colombia_and_costa, lengthen)

ecuador_and_elsalvador <- list(ecuador, elsalvador)
ecuador_and_elsalvador <- map_df(ecuador_and_elsalvador, lengthen)

#guatemala_and_guyana <- list(guatemala, guyana)
#guatemala_and_guyana <- map_df(guatemala_and_guyana, lengthen)

#honduras_and_jamaica <- list(honduras, jamaica)
#honduras_and_jamaica <- map_df(honduras_and_jamaica, lengthen)

guatemala_and_honduras <- list(guatemala, honduras)
guatemala_and_honduras <- map_df(guatemala_and_honduras, lengthen)

mexico_and_nicaragua <- list(mexico, nicaragua)
mexico_and_nicaragua <- map_df(mexico_and_nicaragua, lengthen)

panama_and_peru <- list(panama, peru)
panama_and_peru <- map_df(panama_and_peru, lengthen)

suriname_and_usa <- list(suriname, usa)
suriname_and_usa <- map_df(suriname_and_usa, lengthen)

uruguay_and_venezuela <- list(uruguay, venezuela)
uruguay_and_venezuela <- map_df(uruguay_and_venezuela, lengthen)

paraguay <- lengthen(paraguay)

countries <- list(argentina, belize, bolivia, brazil, canada, chile, colombia, costa, ecuador, elsalvador, guatemala, honduras, mexico, nicaragua, panama, peru, suriname, usa, uruguay, venezuela)

tidy_data <- map_dfr(countries, lengthen)
```

Going to reformat it so that it is easier to read and has informative function name.


#Defining the fucntion
I am renaming the funtion so that it reflects what the function does. 
```{r}
library(tidyr)
library(tidyverse)
library(dplyr)

tidy_spread <- function(x){
  x <- x %>% 
    group_by(column_name) %>%
    mutate(grouped_id = row_number())
  x %>%
    spread(key = column_name, value = answer) %>%
    select(-grouped_id)
}
```

#Pairing Countries - This contains data sets in English and Spanish, jump to line 148 for Spanish-only
```{r}
#First set of four countries
argentina_and_belize <- tidy_spread(argentina_and_belize)
bolivia_and_brazil <- tidy_spread(bolivia_and_brazil)

#Second set of four countries
canada_and_chile <- tidy_spread(canada_and_chile)
colombia_and_costa <- tidy_spread(colombia_and_costa)

#Third set of four countries
ecuador_and_elsalvador <- tidy_spread(ecuador_and_elsalvador)
guatemala_and_guyana <- tidy_spread(guatemala_and_guyana)

#Fourth set of four countries
honduras_and_jamaica <- tidy_spread(honduras_and_jamaica)
mexico_and_nicaragua <- tidy_spread(mexico_and_nicaragua)

#Fifth set of four countries
panama_and_peru <- tidy_spread(panama_and_peru)
suriname_and_usa <- tidy_spread(suriname_and_usa)

#Final set - 3 countries becuase of odd number
uruguay_and_venezuela <- tidy_spread(uruguay_and_venezuela)
paraguay <- tidy_spread(paraguay)
```

#Combining Sets Using `bind_rows()`
```{r}
first_four <- bind_rows(argentina_and_belize, bolivia_and_brazil)
second_four <- bind_rows(canada_and_chile, colombia_and_costa)

third_four <- bind_rows(ecuador_and_elsalvador, guatemala_and_guyana)
fourth_four <- bind_rows(honduras_and_jamaica, mexico_and_nicaragua)

fifth_four <- bind_rows(panama_and_peru, suriname_and_usa)
sixth_four <- bind_rows(fifth_four, uruguay_and_venezuela)
last <- bind_rows(sixth_four, paraguay)
```

#Combining All Sets
```{r}
first_and_second <- bind_rows(first_four, second_four)
third_and_fourth <- bind_rows(third_four, fourth_four)

first_half <- bind_rows(first_and_second, third_and_fourth)
last_combine <- bind_rows(first_half, last)
```


#Writing data into csv file for Tableau
```{r}
write_csv(last_combine, "combined_tidy.csv")
```


##Spanish-only (no Guyana and Jamaica)

#Pairing Countries
```{r}
#First set of four countries
argentina_and_belize <- tidy_spread(argentina_and_belize)
bolivia_and_brazil <- tidy_spread(bolivia_and_brazil)

#Second set of four countries
canada_and_chile <- tidy_spread(canada_and_chile)
colombia_and_costa <- tidy_spread(colombia_and_costa)

#Third set of four countries
ecuador_and_elsalvador <- tidy_spread(ecuador_and_elsalvador)
guatemala_and_honduras <- tidy_spread(guatemala_and_honduras)

#Fourth set of four countries
mexico_and_nicaragua <- tidy_spread(mexico_and_nicaragua)
panama_and_peru <- tidy_spread(panama_and_peru)

#Fifth set of four countries
suriname_and_usa <- tidy_spread(suriname_and_usa)
uruguay_and_venezuela <- tidy_spread(uruguay_and_venezuela)

#Final set - 2 countries becuase of odd number
paraguay <- tidy_spread(paraguay)
```


#Combinig Sets using `bind_rows` Spanish-only
```{r}
first_four <- bind_rows(argentina_and_belize, bolivia_and_brazil)
second_four <- bind_rows(canada_and_chile, colombia_and_costa)

third_four <- bind_rows(ecuador_and_elsalvador, guatemala_and_honduras)
fourth_four <- bind_rows(mexico_and_nicaragua, panama_and_peru)

fifth_four <- bind_rows(suriname_and_usa, uruguay_and_venezuela)
last <- bind_rows(fifth_four, paraguay)
```

#Combining All Sets Spanish-only
```{r}
first_and_second <- bind_rows(first_four, second_four)
third_and_fourth <- bind_rows(third_four, fourth_four)

first_half <- bind_rows(first_and_second, third_and_fourth)
second_half <- bind_rows(first_half, fifth_four)
last_combine <- bind_rows(second_half, last)
```

#Writing data into csv file for Tableau
```{r}
write_csv(last_combine, "spanish_combined_tidy.csv")
```